Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-12-11 WSSSPE3/report/wg_main_best_practices.tex
changed comment to note to make it more actionable

%\subsubsection{Why it is important}
Reviewing multiple past articles and talks at different meetings like WSSSPEx
%\cite{WSSSPE papers, heroux paper, ...} 
and 
analyzing and promoting sustainable scientific software makes it clear that there 
are several common and recurring ideas that underpin success in developing sustainable software. However, outside of a small community, this knowledge is not widely
shared. This is  especially true for the large community of scientists who generate most of the software used by scientists but are not primarily software developers. In this
scenario, a clear and precise exposition of these best practices collected from many sources and open collaboration among all in the community
in a single source (e.g., journal paper, tutorial)  that can be widely disseminated is necessary and likely to be very valuable.

>>>>

%\subsubsection{Why it is important}
Reviewing multiple past articles and talks at different meetings like WSSSPEx \todo{add cites to WSSSPE papers, heroux paper, ...} 
and 
analyzing and promoting sustainable scientific software makes it clear that there 
are several common and recurring ideas that underpin success in developing sustainable software. However, outside of a small community, this knowledge is not widely
shared. This is  especially true for the large community of scientists who generate most of the software used by scientists but are not primarily software developers. In this
scenario, a clear and precise exposition of these best practices collected from many sources and open collaboration among all in the community
in a single source (e.g., journal paper, tutorial)  that can be widely disseminated is necessary and likely to be very valuable.
